STAT 450 Project: Real Estate

### 2020-03-31 src/2nd_draft.Rmd

@@

@@

                    Table 4: Data with missing mill rate

>>>>

For predicted mill rate in 2020, please refer to **Appendix** Table 4.

@@

### 2020 Mill Rate prediction

```{r, echo=FALSE, warning=FALSE}
mill_rate_pre_2020 <- read.csv(here("data","assessment_2020_fit.csv"))[,-c(1,2,5)]
```

                Table 4: Predicted Mill Rate in 2020 based on transformed model (%)

Municipality | Residential (%) | Light industry (%) | Business (%)                      
------|------|------|------
Anmore | 0.98 | NA | 9.91
Belcarra | 1.19 | NA | 12.31
Bowen Island | 1.63 | 14.69 | 11.15
Burnaby | -2.76 | 12.80 | 10.88
Coquitlam | 1.72 | 17.70 | 12.84
Delta | 5.50 | 12.98 | 13.65
Langley - City | 1.73 | 15.12 | 12.25
Langley - Township | 3.77 | 12.46 | 12.49
Lions Bay | 2.19 | NA | 11.66
Maple Ridge | 5.11 | 16.88 | 13.60
New Westminster | 4.65 | 18.04 | 15.78
North Vancouver - City | -2.17 | 15.51 | 11.90
North Vancouver - Dist | 1.29 | 13.68 | 11.82
Pitt Meadows | 6.06 | 17.00 | 13.78
Port Coquitlam | 4.91 | 17.58 | 14.50
Port Moody | 4.16 | 17.66 | 13.44
Richmond | 1.14 | 10.42 | 10.29
Surrey | 0.82 | 12.47 | 10.53
Vancouver | 2.69 | 12.38 | 8.79
West Vancouver | 4.92 | 17.05 | 12.62
White Rock | 1.88 | 16.33 | 12.17

@@

                          Table 5: Data with missing mill rate
